### 2013-09-24 evaluation/paper.tex
caption below tables
snakes and msrc plots

\begin{table}
    \caption{Summary of Datasets.\tablabel{datasets}}
    \begin{tabu} to \linewidth{@{}X[1,l]YX[1,c]X[1,c]YY@{}}
    %\multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\
    \toprule
    Dataset    & {samples} & nodes & edges & {dim w} & {labels}\\
    \cmidrule{1-6}
    MNIST      & 60000   & 1     & none  & 7840  & 10\\
    OCR-small  & 704     & 3--14 & chain & 1444  & 26\\
    OCR-large  & 6173    & 3--14 & chain & 1444  & 26\\
    scene-tree & 1211    & 6     & tree  & 1244  & 2\\
    scene-full & 1211    & 6     & loopy & 1284  & 2\\
    yeast-tree & 1500    & 14    & tree  & 1494  & 2\\
    yeast-full & 1500    & 14    & loopy & 1806  & 2\\
    snake      & 200     &84--168& loopy & 22275 & 11\\
    MSRC21     & 276     & 7--113& loopy &  1764 & 21\\
    Pascal VOC & 964     & 8--112& loopy &  2646 & 21\\
    \bottomrule

    \end{tabu}
\end{table}

@@

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/scene_tree_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/scene_tree_log_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/scene_full_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/scene_full_log_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree_log_time}
    \end{tabu}
\caption{%
   Convergence of the primal objective on the multi-label datasets. From top to
   bottom: the scene dataset using a tree model, the scene dataset using a full
   model, the yeast dataset using a tree model, and the yeast dataset using a
   full model.
\figlabel{multi-label-results}}
\end{figure}

@@

>>>>

\begin{table}
    \begin{tabu} to \linewidth{@{}X[1,l]YX[1,c]X[1,c]YY@{}}
    %\multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\
    \toprule
    Dataset    & {samples} & variables & graph & {dim $\theta$} & {labels}\\
    \cmidrule{1-6}
    MNIST      & 60000   & 1     & none  & 7840  & 10\\
    OCR-small  & 704     & 3--14 & chain & 1444  & 26\\
    OCR-large  & 6173    & 3--14 & chain & 1444  & 26\\
    scene-tree & 1211    & 6     & tree  & 1244  & 2\\
    scene-full & 1211    & 6     & loopy & 1284  & 2\\
    yeast-tree & 1500    & 14    & tree  & 1494  & 2\\
    yeast-full & 1500    & 14    & loopy & 1806  & 2\\
    snake      & 200     &84--168& loopy & 22275 & 11\\
    MSRC21     & 276     & 7--113& loopy &  1764 & 21\\
    Pascal VOC & 964     & 8--112& loopy &  2646 & 21\\
    \bottomrule
    \end{tabu}
    \caption{Summary of datasets used in the evaluation. \tablabel{datasets}}
\end{table}

@@

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/scene_tree_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/scene_tree_log_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/scene_full_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/scene_full_log_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree_log_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree_log}&%
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree_log_time}
    \end{tabu}
\caption{%
   Convergence of the primal objective on the multi-label datasets. From top to
   bottom: the scene dataset using a tree model, the scene dataset using a full
   model, the yeast dataset using a tree model, and the yeast dataset using a
   full model.
\figlabel{multi-label-results}}
\end{figure}

@@

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_ad3_time_loss}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/snakes_qpbo_time_loss}
    \end{tabu}
\caption{%
    Snakes
\figlabel{snakes_results}}
\end{figure}

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \multicolumn{2}{@{}c@{}}{\includegraphics[width=\linewidth]{evaluation/legend.pdf}}\\[-3mm]
    \includegraphics[width=\linewidth]{evaluation/images/msrc}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/msrc_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time_loss}\\
    \includegraphics[width=\linewidth]{evaluation/images/msrc}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time}\\
    \includegraphics[width=\linewidth]{evaluation/images/msrc_loss}&%
    \includegraphics[width=\linewidth]{evaluation/images/msrc_time_loss}
    \end{tabu}
\caption{%
    MSRC, Pascal VOC
\figlabel{msrc_pascal}}
\end{figure}

### 2013-09-24 pystruct/paper.tex
snakes and msrc plots

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the popular Pascal dataset. Details of the experiment
can be found in Chapter~\ref{exact_learning}.
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')

>>>>

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the Pascal dataset. Details of the experiment
can be found in Section~\secref{semantic_segmentation}.
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')
